\textbf{\sc Towards Deliberative Control of Autonomous Robots}

### 2012-02-06 europa-basics.tex
updates

\eu is a versatile planning framework, let's start by looking at some examples of the main problem types that it can tackle.

@@

A constraint programming problem consists of a set of variables $V=
{x_1,..,x_N}$, where each variable takes values from a domain
$d_1,..,d_N$; in this chapter we will deal only with discrete and
finite domains. Given a defined conjunctive set of constraints on the
variables: $C=\{c_1(x_1,..,x_N), ..., c_K(x_1,..,x_N)\}$, the objective
is to find one or more value assignments to $V$ where all constraints
are satisfied.

To solve a problem, CP techniques use logical inference to perform Constraint Propagation, which consists of two
operations:

@@

A set of constraints and variables that describe a problem domain are typically represented as a Constraint Network, where the variables are nodes , and constraints are arcs between the variables. Having this network representation in mind, Arc Consistency for a a pair of variables x,y is achieved if for every value in x's domain, there is a value in the y's domain that is consistent with all the constraints that connect x and y. 
A naive approach to ensuring arc consistency consists of cycling through all the variable pairs and performing constraint propagation until there are no variable domain changes, the AC-3 algorithm \comment {citation [MAC77]} improves over the naive approach by ignoring constraints whose variables were not affected since the last iteration. AC-3 is very popular in CP implementations.

Arc Consistency and other, more sophisticated consistency algorithms \comment {citation CP Handbook} can be used to efficiently prove that a CP problem is unsatisfiable, however, they generally can't prove that a CP problem is satisfiable and provide specific variable assignments that constitute solutions. For that, search algorithms like global backtracking or local search are used \comment {citation CP Handbook}, which use consistency as an efficient way to prune the search space.

In theory, solving a CP problem is NP-Hard \cite{ghallab04}, but often very efficient in practice using a number of consistency and search algorithms that are well understood.

@@

Constraint-based Planning and specifically Constraint-Based Attribute
and Interval planning (CAIP) \cite{mus94,frank2003} is intended to
close that gap. On one hand, it takes advantage of a CSP
representation; one the other it also uses attributes and intervals to
maintain an explicit representation of the elements relevant to
planning. This makes it easier to write algorithms that search for an
reason abut plans. The main elements of CAIP are:

@@

TODO: talk about actions

@@

For example, consider the tire-world domain. The tire was located in
the trunk with the predicate tireLocated(Trunk) and located on the
ground with the predicate tireLocated(Ground). Clearly, the same tire
cannot be in both places at once. A Timeline provides a simple method
for aggregating the statements about a tire such that they are
mutually exclusive.

>>>>

At the core of the \rx framework, is the deliberation engine, \eu,
which has a rich legacy from NASA missions. \eu is a versatile
Constraint-based temporal planner which continues to be deployed on a
diverse set of applications. We motivate this section with some
problem domains this planner can handle and then delve in substantial
detail.

% \eu is a versatile planning framework.  let's start by looking at some examples of the main problem types that it can tackle.

@@

A constraint programming problem consists of a set of variables $V=
{x_1,..,x_N}$, where each variable takes values from a domain
$d_1,..,d_N$; in this chapter we will deal only with discrete and
finite domains. Given a defined conjunctive set of constraints on the
variables: $C=\{c_1(x_1,..,x_N), ..., c_K(x_1,..,x_N)\}$, the
objective is to find one or more value assignments to $V$ where all
constraints are satisfied. To solve a problem, CP techniques use
logical inference to perform Constraint Propagation, which consists of
two operations:

@@

A set of constraints and variables that describe a problem domain are
typically represented as a Constraint Network, where the variables are
nodes and constraints are arcs between the variables. Having this
network representation in mind, Arc Consistency \comment{needs a
  definition} for a pair of variables $x,y$ is achieved if for every
value in $x$'s domain, there is a value in $y$'s domain that is
consistent with all the constraints that connect $x$ and $y$.  A naive
approach to ensuring arc consistency consists of cycling through all
the variable pairs and performing constraint propagation until there
are no variable domain changes. The AC-3 algorithm \cite{mackworth77},
a popular implementation, improves over the naive approach by ignoring
constraints whose variables were not affected since the last
iteration.

Arc Consistency and other sophisticated consistency algorithms can be
used to efficiently prove that a CP problem is unsatisfiable. However,
they generally cannot prove that a CP problem is satisfiable and
provide specific variable assignments that constitute solutions. For
that, search algorithms like global backtracking \comment{citation
  needed} or local search are used; these use consistency as an
efficient way to prune the search space \comment {citation CP
  Handbook}. In theory, solving a CP problem is NP-Hard
\cite{ghallab04}, but often very efficient in practice using a number
of consistency and search algorithms that are well understood.

@@

Constraint-based Planning and specifically Constraint-Based Attribute
and Interval planning (CAIP) \cite{mus94,frank2003} is intended to
close that gap. On one hand, it takes advantage of a CSP
representation; on the other it uses attributes and intervals to
maintain an explicit representation of the elements relevant to
planning. This makes it easier to write algorithms that search for an
reason abut plans. The main elements of CAIP are:

@@

\comment{talk about actions}

@@

\comment{This is the first instance that this domain is being
  introduced. Either we need more explanation or it ought to be
  removed.} For example, consider the tire-world domain. The tire was
located in the trunk with the predicate tireLocated(Trunk) and located
on the ground with the predicate tireLocated(Ground). Clearly, the
same tire cannot be in both places at once. A Timeline provides a
simple method for aggregating the statements about a tire such that
they are mutually exclusive.
